Regularising Lotka--Volterra interaction matrices by species grouping: optimal groupings are unpredictable

### 2022-02-22 article.rnw
Put all invocations of `source` in the R code of article.rnw in the same place.

<<include=FALSE>>=
	source("r/post-process.R")
	source("r/brute-post-process.R")

@@

	brute_data <- BruteData$new("output/brute.data", species_names)

	source("r/coclassification-table.R")
@

>>>>

<<include=FALSE>>=
	source("r/post-process.R")
	source("r/brute-post-process.R")
	source("r/coclassification-table.R")

@@

	brute_data <- BruteData$new("output/brute.data", species_names)
@
